%Schedule 2015
\clearpage
%\newpage
\section{Proposed Reading \& Seminar Schedule}	

\subsection{\textbf{Week 1}: My Ecotopia}

\paragraph{Seminar --- Tuesday, August 30}

\begin{itemize*}

\item \href{http://video.foxbusiness.com/v/4184405298001/californias-drought-a-man-made-crisis/?#sp=show-clips}{Environmentalists Cause Drought}		
  \item \href{http://video.foxbusiness.com/v/2016991509001/government-using-endangered-species-act-against-oil-industry/?#sp=show-clips}{ESA as a weapon}	
    \item Environmental Monitoring and Sentinels
    \item First Meeting	
    
    %			\item \href{https://www.youtube.com/watch?v=0gDErDwXqhc}{Skeptic's Case}
      %			\item \href{https://www.youtube.com/watch?v=BSKVqQK-7pE&feature=youtu.be}{Hutton Interview}
      
      \item Discussion of Course Design and Syllabus
      \item History of ESA
      \end{itemize*}
      
    
      \paragraph{Seminar --- Thursday, September 1}
      
      \begin{itemize*}
      \item Kolbert, E. 2014. The Sixth Extinction: An unnatural history. Prologue-Chapter V.
      \item Dobson, AP, et al. 1997. Geographic distribution of endangered species in the United States. Science 275(5299):550-553.
      \end{itemize*}
      

      \subsection{\textbf{Week 2}: Freshwater Habitat and Resource Decision Making}
      
      \paragraph{Seminar --- Tuesday, September 6}
      
      \begin{itemize*}
      \item Poff, N. 2003 River flows and water wars: Emerging science for environmental decision making. Frontiers in Ecology and the Environment 1(6):298-306.
      \item Karr, Interlandi, and Houtman. 2015. Environmental Science. Second Edition. Chapter 15. Water Pollution (pp. 278-297).
      \item Artiola, J, Pepper, IL, Brusseau, M. 2004. Environmental Monitoring and Characterization. Chapter 9. Monitoring Surface Waters (pp. 141-161).
      
      \end{itemize*}
    
      
      \paragraph{Seminar --- Thursday, September 8}
      
      \begin{itemize*}
      \item Martin, T. 2012. Eliciting expert knowledge in conservation science. Conservation Biology 26(1):29-38.
      \item Kolbert, E. 2014. The Sixth Extinction: An unnatural history. Chapter VI-Chapter XIII.
      \end{itemize*}
      

      
      \subsection{\textbf{Week 3}: Habitat Quality}
      
      \paragraph{Seminar --- Tuesday, September 13}
      
      \begin{itemize*}
      \item Straight, S. 2015. Santa Ana River. Orion Magazine 34(1):21-XX.
      \item Gandy M. 2006. Riparian Anomie: Reflections on the Los Angeles River. Landscape Research 31(2):135-145.
      \end{itemize*}
      

      
      \paragraph{Seminar --- Thursday, September 15}
      
      \begin{itemize*}
      \item R\'{o}zsa, L and Zolt\'{a}n V. 2015. Co-extinct and critically co-endangered species of parasitic lice, and conservation-induced extinction: should lice be reintroduced to their hosts? Oryx 49(1): 107-110.
      \end{itemize*}
      

    
    
    \subsection{\textbf{Week 4}: Community Profiling using Molecular Biology Tools}
    
    \paragraph{Seminar --- Tuesday, September 20}
    
    \begin{itemize*}
    \item Kysar, DA. 2010. Regulating from Nowhere: Environmental Law and the Search 
    \href{https://books.google.com/books?isbn=0300163304}{} 
    \item Passalacqua, NG 2015. On the definition of element, chorotype and component in biogeography. Journal of Biogeography 42(4)611-6
    \item Pungetti, G, G Oviedo, and D Hooke. 2012. Chapter 17 Maori and Lizards IN Sacred Species and Sites: Advances in Biocultural Conservation. Cambridge University Press, Nature X:XXX
    \end{itemize*}
    

    
    
    \paragraph{Seminar --- Thursday, September 22}		
    
    \begin{itemize}
    \item Houck, Oliver A. 1994. Why Do We Protect Endangered Species, and What Does That Say about Whether Restrictions on Private Property to Protect Them Constitute Takings. Iowa L. Rev. 80:297.
    \end{itemize}
    
    
    \subsection{\textbf{Week 5}: Knowledge Production and Litigation}
    
    \paragraph{Seminar --- Tuesday, September 27}		
    
    
    No Class  % Board of Forestry and Fire Protection -- Field Trip, Humbolt County
    

      
      \paragraph{Seminar --- Thursday, September 29}
      
      \begin{itemize*}
      \item A Civil Action
      \end{itemize*}
      

      
      % Week 6
      \subsection{\textbf{Week 6}: Environmental Health and Risks}
      
      \paragraph{Seminar --- Tuesday, October 4}
      
      \begin{itemize*}
      \item Fagan, D. 2013. Toms River. Chapters 1-7 (xi-134 pp).
      \end{itemize*}
      

      
      \paragraph{Seminar --- Thursday, October 6}
      
      \begin{itemize*}
      \item Davies, K. 2013. The Rise of the U.S. Environmental Health Movement. Chapter 1-3 (pp. 1-62).	
      \end{itemize*}
      
      
      
      % Week 7		
      \subsection{\textbf{Week 7:} Environmental Health Hazards}
      
      \paragraph{Seminar --- Tuesday, October 11}
      
      \begin{itemize*}
      %\item Karr, Interlandi, and Houtman. 2015. Environmental Science. Second Edition. Chapter 1-2 (pp. 2-39).
      \item Fagan, D. 2013. Toms River. Chapters 8-13 (137-248 pp).
      \item Kriebel, David. 2001. The Precautionary Principle in Environmental Science. Environmental Health Perspectives 109:871-876.
      %\item Tufte, E. 1997. Visual and Statistical Thinking. Graphic Press. LLC, Cheshire, CT.	
      \end{itemize*}
      

      
      \paragraph{Seminar --- Thursday, October 13}
      
      \begin{itemize*}
      %\item Davies, K. 2013. The Rise of the U.S. Environmental Health Movement. Chapter 1-3 (pp. 1-62).
      \item TBD			
      \end{itemize*}
    
      
      
      \subsection{\textbf{Week 8}: Hazards and Class}
      
      \paragraph{Fall Recess --- Tuesday, October 18}
    
      
      \paragraph{Seminar --- Thursday, October 20}
      
      \begin{itemize*}
      %\item Davies, K. 2013. The Rise of the U.S. Environmental Health Movement. Chapter 1-3 (pp. 1-62).
      
      \item Fagan, D. 2013. Toms River. Chapters 14-19 (pp. 251-360 ).
      \item Kriebel, David. 2001. The Precautionary Principle in Environmental Science. Environmental Health Perspectives 109:871-876.					
      \end{itemize*}
      
      
      \subsection{\textbf{Week 9:} Risk and Clusters}
      
      \paragraph{Seminar --- Tuesday, October 25}
      
      \begin{itemize*}
      %\item Davies, K. 2013. The Rise of the U.S. Environmental Health Movement. Chapter 1-3 (pp. 1-62).	
      \item Fagan, D. 2013. Toms River. Chapters 20-24 (363-462 pp).
      \item Wartenberg, D. 2001. Investigating Disease Clusters: Why, When and How? Analysis and Interpretation of Disease Clusters and Ecological Studies. Journal of the Royal Statistical Society. Series A (Statistics in Society) 164(1):13-22.
      \end{itemize*}
      
      \paragraph{Seminar --- Thursday, October 27}
      
      \begin{itemize*}
      \item TBD
      \end{itemize*}
      
      \subsection{\textbf{Week 10:} Mapping the Environment}
      
      \paragraph{Seminar --- Tuesday, November 1}
      
      % Board of Forestry and Fire Protection
      \begin{itemize*}
      \item tbd
      \end{itemize*}
    
      
      \paragraph{Seminar --- Thursday, November 3}
      
      \begin{itemize*}
      \item \href{https://www.youtube.com/watch?v=6yiTZm0y1YA&feature=youtu.be}{IPCC Climate Change Evidence}
      \item \href{https://www.youtube.com/watch?v=0gDErDwXqhc}{Skeptic's Case}
    \item \href{https://www.youtube.com/watch?v=BSKVqQK-7pE&feature=youtu.be}{Hutton Interview}
    \end{itemize*}
    
    
    \subsection{\textbf{Week 11}: Epistemology and the Environment}
    
    \paragraph{Seminar --- Tuesday, November 8}
    
    \begin{itemize*}
    \item Buttel and Taylor. 1992. How do we know we have global environmental problems. Geoforum 23(3):405-416.
    \item Schneider, S. 2009. The worst-case scenario. Nature 458:1104-1105.
    \item Peterson, TC, Connolley, WM. and Fleck, J. 2008. The Myth of the 1970s Global Cooling Scientific Consensus. American Meteorological Society. 9:1325-1337.
    \end{itemize*}

    
    \paragraph{Seminar --- Thursday, November 10}
    
    \begin{itemize*}
    \item test	
    \end{itemize*}	
    
    \subsection{\textbf{Week 12}: Temperature Records}
    
    \paragraph{Seminar --- Tuesday, November 15}
    
    \begin{itemize*}
    \item test
    \end{itemize*}
    
    
    \paragraph{Seminar --- Thursday, November 17}
    
    \begin{itemize*}
    \item tbd
    \end{itemize*}	
    
    \subsection{\textbf{Week 13}: Tensions}
    
    \paragraph{Seminar --- Tuesday, November 22}
    
    \begin{itemize*}
    \item tbd
    \end{itemize*}
    
    
    \paragraph{Thanksgiving Recess --- Thursday, November 24}
    
    \subsection{\textbf{Week 14}: Use and Abuse of Data in Environmental Science}
    
    \paragraph{Seminar --- Tuesday, November 29}
    
    \begin{itemize*}
    \item TBD
    \end{itemize*}	
    

    \paragraph{Seminar --- Thursday, December 1}
    
    \begin{itemize*}
    \item TBD
    \end{itemize*}
    
    
    \subsection{\textbf{Week 15}: Critical Utopia}
    
    \paragraph{Seminar --- Tuesday, December 6}
    
\begin{itemize*}
  \item Final Paper Workshop
\end{itemize*}

    \paragraph{Final Paper Due --- Wednesday, December 7}   
   